Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 conclusion.tex
yes

Building on previous work to define requirements for
visual analytics, we designed an environment
for exploration, sharing, presentation and publishing.
We implemented it in the RCloud prototype.

We deployed RCloud in a community of working data scientists.
Experience with the prototype provides evidence that data
science teams and the organizations in which they work benefit from
having capabilities to support collaboration and to integrate
the entire visual analytics process. We found that features for
sharing and publishing were eagerly adopted. Features for 
single-user data exploration, that compete with existing mature
tools, were not accepted as readily. Some experienced users
fashioned their own workflow so they could keep using familiar EDA tools.

>>>>

Building on previous work to define requirements for
visual analytics, we designed an environment
for exploration, sharing, presenting and publishing.
We implemented it in the RCloud prototype.

We deployed RCloud in a community of working data scientists.
Experience with the prototype provides evidence that data
science teams and the organizations in which they work benefit from
capabilities to support collaboration and to integrate
the entire visual analytics process. We found that features for
sharing and publishing were eagerly adopted. Features for 
single-user data exploration, that compete with existing mature
tools, were not accepted as readily. Some experienced users
fashioned their own workflow so they could keep using familiar EDA tools.
